ESRC SDAI Application

### 2019-05-17 Draft.tex
update

Aim 2: The timecourse of abuse. The decision to report. Breaking point theory - do we see a long string of abuse being reported after certain days (Xmas, Valentine’s day)? Hazard model? Tim knows the birthdays. Separation.

>>>>

Increasing victim's willingness to report domestic abuse is key in reducing prevalence and preventing escalation into domestic homicides. Our unique crime dataset will allow us to follow victim-offender pairs over time and explore how the severity and nature of reported abuse changes over time.

We will also be able to identify high-risk days of the year (e.g., birthdays, Christmas, Halloween) by the characteristics of the victim-offender pair and the pattern and duration of abuse. Insights from this investigation can inform decisions about the optimal timing and target audience for domestic abuse awareness campaigns.

Separation is one of the biggest predictors of abuse resulting in serious injury. Subject to whether we can get data on the DVPOs (Domestic Violence Protection Order) and DVPNs (Domestic Violence Protection Notice) issued in the West Midlands in the relevant period, we could explore the offender characteristics that predict the likelihood of sustained perpetration after separation, and assess the overall efficacy of these new preventive measures.

 Hazard model?
